---
title: "R Notebook"
output:
  html_document:
    df_print: paged
---


# Load Libraries 

```{r, warning=FALSE, message=FALSE}
library(tidyverse)
library(tidymodels)
library(janitor)
library(skimr)
library(kableExtra)
library(GGally)
library(fastshap)   
library(MASS)
library(ISLR)
library(ggplot2)
library(dplyr)
library(lubridate)
library(imputeTS)
library(forecast)
library(urca)
library(pracma)
library(astsa)
library(fpp2)

```

# Load Data
```{r}
rs<-read_csv("RetailSales2.csv") %>%
  clean_names()

head(rs)
lace <- subset(rs, select=c(laces))
blouse<-subset(rs, select=c(blouses))
```

# For lace
## Time series
seasonal but no trend
```{r}
lace_ts <- ts(lace, start=c(1994,1), frequency = 12)
plot(lace_ts)
```

## ACF/PACF
```{r}
ggAcf(lace_ts, lag.max=200)

ggPacf(lace_ts, lag.max=200)
```

## ADF 
```{r}
lace_df <- ur.df(lace_ts, type = "drift")
summary(lace_df)
```

## Take a 12-month seasonal difference and look at ACF and PACF
```{r}
lace_12 <- diff(lace_ts,12)
ggAcf(lace_12)
ggPacf(lace_12)
```


## Model 1 ETS
```{r}
lace_ets <- ets(lace_ts, model="ZZZ")
summary(lace_ets)
checkresiduals(lace_ets)

forecast(lace_ets, h=3)

lace_ets %>% forecast() %>% autoplot()
```

## Model 2 - Additive Holt Winter
```{r}
laceA <- hw(lace_ts, seasonal="additive", h=12)
summary(laceA)
checkresiduals(laceA)
forecast(laceA, h=3)
laceA %>% forecast() %>% autoplot()
```

##  Model 3 - Multiplicative Holt Winter
```{r}
laceM <- hw(lace_ts, seasonal="multiplicative", h=12)
summary(laceM)
checkresiduals(laceM)
forecast(laceM, h=3)
laceM %>% forecast() %>% autoplot()

```

## Mod 4 - ARiMA
```{r}
fit_auto2 <- auto.arima(lace_ts)
summary(fit_auto2)
checkresiduals(fit_auto2)
accuracy(fit_auto2)
forecast(fit_auto2, h=3)
fit_auto2 %>% forecast() %>% autoplot()
```



# For blouse
## Time series
seasonal and trend
```{r}
blouse_ts <- ts(blouse, start=c(1994,1), frequency = 12)
plot(blouse_ts)
```

## ACF/PACF
```{r}
ggAcf(blouse_ts, lag.max=200)

ggPacf(blouse_ts, lag.max=200)
```

## ADF 
```{r}
blouse_df <- ur.df(blouse_ts, type = "drift")
summary(blouse_df)
```

## Take a 12-month seasonal difference and look at ACF and PACF
```{r}
blouse_12 <- diff(blouse_ts,12)
ggAcf(blouse_12)
ggPacf(blouse_12)
```


## Model 1 ETS
```{r}
blouse_ets <- ets(blouse_ts, model="ZZZ")
summary(blouse_ets)
checkresiduals(blouse_ets)
forecast(blouse_ets, h=3)
blouse_ets %>% forecast() %>% autoplot()
```

## Model 2 - Additive Holt Winter
```{r}
blouseA <- hw(blouse_ts, seasonal="additive", h=12)
summary(blouseA)
checkresiduals(blouseA)
forecast(blouseA, h=3)
blouseA %>% forecast() %>% autoplot()
```

##  Model 3 - Multiplicative Holt Winter
```{r}
blouseM <- hw(blouse_ts, seasonal="multiplicative", h=12)
summary(blouseM)
checkresiduals(blouseM)
forecast(blouseM, h=3)
blouseM %>% forecast() %>% autoplot()

```

## Mod 4 - ARiMA
```{r}
fit_auto <- auto.arima(blouse_ts)
summary(fit_auto)
checkresiduals(fit_auto)
accuracy(fit_auto)
forecast(fit_auto, h=3)
fit_auto %>% forecast() %>% autoplot()
```
